Using Scipion for Stream Image Processing at Cryo-EM Facilities

### 2018-04-23 1.introduction.tex
I think this is done except for the cover letter

3D electron microscopy (3DEM)  can provide rich information about structural characteristics of macromolecular complexes. The field is under a major transformation due to the arrival of better microscopes, new large area direct electron detectors and automation \citep{kuhlbrandt2014a, Kuhlbrandt2014b}. These improvements make possible that a single microscope generates high quality data sets on the order of terabytes per day \citep{Saibil2015} while working for several days without interruption. Major challenges faced in the field are: (1) an efficient management of these huge datasets and their corresponding image processing workflows; (2) a raising interest from scientists outside the field who might lack the skills of a experienced microscopist and; (3) the need for an effective data and metadata transfer in an increasingly distributed and collaborative environment. %This situation strongly demands the application of techniques that are highly automated to allow high throughput.

@@

For most cases, the future of projects that require high-end microscopes is through centralized microscopy facilities, in which automatically acquired data needs to be monitored by users and facility staff.  With this scenario in mind, we have redesigned \scipion which is a software framework for integrating several 3DEM software packages through a workflow-based approach \citep{delarosatrevin2016}. % in which the early detection of issues may save a data acquisition shift which otherwise needs to be repeated after a new application that may be granted many months later. 
In this way, \scipion starts the processing of the movies as they are being acquired with the double aim of checking for possible data collection errors and execute a first user-tailored image processing workflow that provides users with an accurate estimation of the acquired data quality.

Many software packages have been developed to provide automated data collection, such as SerialEM \citep{Mastronarde2005}, Leginon \citep{Suloway2009}, UCSF-Tomography \citep{Zheng2007}, Tom Toolbox \citep{Nickell2005}, EPU \citep{EPU}, Latitude in Digital Micrograph \citep{Latitude}, EMMenu \citep{emmenu}, etc. However, the next step,  which is to provide image processing while  data are being collected, is not so well addressed. In fact, in most places this is accomplished through home made scripts \citep[e.g.][]{Pichkur2018}. %(i.e. \citet{Pichkur2018}).
Exceptions are UCSFImage4 \citep{Li2015}, Focus \citep{Biyani2017} and Relion \citep{fernandez2017:relion-pipeline}. As we will show in this article, \scipion differs from these solutions in a larger flexibility, both from the point of view of users and facility staff.

>>>>

3D electron microscopy (3DEM)  can provide rich information about structural characteristics of macromolecular complexes. The field is under a major transformation due to the arrival of better microscopes, new large area direct electron detectors and automation \citep{kuhlbrandt2014a, Kuhlbrandt2014b}. These improvements make possible that a single microscope generates high quality data sets on the order of terabytes per day \citep{Saibil2015} while working for several days without interruption. Major challenges faced in the field are: (1) an efficient management of these huge datasets and their corresponding image processing workflows; (2) the need for sharing data and metadata  in an increasingly distributed and collaborative environment and; (3) a raising interest from scientists outside the field who might lack the skills of a experienced microscopist. %This situation strongly demands the application of techniques that are highly automated to allow high throughput.

@@

For most cases, the future of projects that require high-end microscopes is through centralized microscopy facilities, in which automatically acquired data needs to be monitored by users and facility staff.  With this scenario in mind, we have redesigned \scipion which is a software framework for integrating several 3DEM software packages through a workflow-based approach \citep{delarosatrevin2016}. % in which the early detection of issues may save a data acquisition shift which otherwise needs to be repeated after a new application that may be granted many months later. 
In this way, \scipion starts the processing of the movies as they are being acquired with the double aim of checking for possible data collection errors and executing a first user-tailored image processing workflow that provides users with an accurate estimation of the acquired data quality.

Many software packages have been developed to support automated data collection, such as SerialEM \citep{Mastronarde2005}, Leginon \citep{Suloway2009}, UCSF-Tomography \citep{Zheng2007}, Tom Toolbox \citep{Nickell2005}, EPU \citep{EPU}, Latitude in Digital Micrograph \citep{Latitude}, EMMenu \citep{emmenu}, etc. However, the next step,  which is to provide image processing while  data are being collected, is not so well addressed. In fact, in most places this is accomplished through home made scripts \citep[e.g.][]{Pichkur2018}. %(i.e. \citet{Pichkur2018}).
Exceptions are UCSFImage4 \citep{Li2015}, Focus \citep{Biyani2017} and Relion \citep{fernandez2017:relion-pipeline}. As we will show in this article, \scipion differs from these solutions in a larger flexibility, both from the point of view of users and facility staff.

### 2018-04-23 2.overall.tex
I think this is done except for the cover letter

In the following we describe the most important modifications made to \scipion in order to facilitate its deployment and execution in centralized facilities.

\subsection{Stream Processing}
The main change introduced in \scipion is \emph{stream processing}, that is, computing on data directly as they are produced or received.
In this way, a new level of parallelization has been reached since the  data generated by the microscope continuously flows through a chain of protocols. For example, as movies are imported to the system they are aligned and their CTF is estimated. In \scipion version 1.2, users may find  the first steps in the image processing workflow adapted to streaming, including movie alignment,  CTF estimation and particle picking and extraction. In the developers version, several 2D classification algorithms are being adapted for this new way of processing.

%\scipion is a multilayered application, the first layer handles the interaction with the user (\emph{presentation layer}), the second saves and retrieves the data used by the application  (\emph{data layer}) and finally, the third layer (\emph{business layer}) process the data following the user instructions.  
\scipion stream implementation make extensive use of threads. %A thread is the smallest unit of processing that can be scheduled by an operating system. 
Using threads, a programmer can effectively create two or more tasks that run at the same time and share the protocol resources (i.e. memory). 
%is based on periodic updates of the protocol input and output data during the image processing. 
%Each protocol execution in \scipion is an independent process that can create processing threads. 
Each protocol that works in streaming mode has one of its threads monitoring input and updating output  data while other threads take care of the data processing. This clear separation between data access and data processing marks an important difference between running a script or using \scipion, since it facilitates a form of computing in which several jobs are executed  concurrently, instead of sequentially. Moreover, \scipion workflow engine allows users to modify the workflow on the fly without modifying a single line of code.
%In practice, the latter follows  a more general and extensible approach that allows users to modify the workflow on the fly without modifying a single code line. %Moreover, it also allows to quickly develop new workflows .

@@

The second set of metaprotocols are grouped under the name \emph{consensus}. For a given logical step (for example, particle picking) these protocols check if the datasets obtained from the same input data using a different algorithm are consistent. Continuing with the particle picking example, \protocol{consensus picking} will compare, at a given instant, the particles selected for each one of the executed particle-picking algorithms and produce as output a particle set containing those particles selected by most of the algorithms.

We would like to finish this section stressing that despite the modifications introduced to \scipion data and process model, the framework keeps providing full data provenance and backward compatibility. That is, \scipion provides detailed information about the origin of the data  and the process to generate it.

@@

\scipion is a flexible framework that allows to create different workflows by choosing among many algorithms at each step. In this work we do not recommend a particular workflow  over others since we realize that different specimens, microscopes or facilities may have different requirements. Nevertheless, since a use case may clarify \scipion capabilities, in the following we describe the pipeline offered by default at the \emph{National Center for Biotechnology} (CNB) cryoEM Facility.

The workflow starts two independent protocols in parallel. The first protocol estimates the camera gain at each pixel for a few  movies \citep{sorzano2018}. % In the CNB setup the microscope camera is calibrated and internally performs the gain correction before writing the movies so the estimated gain image should be almost constant and equal to 1. 
The output of this protocol serves as verification of the validity of the experimental gain image for the whole data set. The second protocol performs direct detector movie alignment. Currently \scipion offers  five  methods for movie alignment: motioncorr \citep{Li2015}, motioncor2 \citep{Zheng2016:motioncor2}, correlation (an unpublished CPU version that implements in Xmipp a global alignment method and solves it similarly to motioncorr but using robust statistics), unblur \citep{Grant2015:unblur} and optical flow \citep{Abrishami2015:optical-flow}. Then the CTF of the resulting micrographs are calculated. Scipion provides three CTF estimation methods:
CTFFIND4 (Rohou and Grigorieff, 2015), gCTF (Zhang, 2016) and Xmipp CTF estimation (Sorzano et al., 2007; Vargas et al., 2013). At this point the user may compute the CTFs using several algorithms and compare them with the protocol \protocol{CTF consensus} that reports up to which frequency two estimation of the same micrograph are equivalent. Further automatic filtering based on CTF is available through the protocol \protocol{CTF filtering} that selects micrographs based on the astigmatism, resolution and defocus. %Another criteria for CTF selection is iciness, that is,  the ratio of the intensity in the resolution band between 3.5 and 3.9 \AA, and between 6 and 30 \AA, which gives a good estimate of the ice crystal content of the vitreous specimen.

Up to this point the image processing pipeline is quite solid and may be executed in streaming without user intervention. The next step is to select (pick) particles. We have recently adapted eight particle picking methods in \scipion  to streaming. In this way,  particles may be selected as soon as any new micrograph is available. Some picking algorithms require a training step in which either user intervention or information from a previous selection is needed. The streaming functionality is separated from the picking logic, so if in the future a new algorithm is added, it will work in streaming without extra effort from the algorithm developer. For those users that execute several picking algorithms, the protocol \protocol{picking consensus} may be useful. \protocol{picking consensus}  calculates the agreement between different particle-picking algorithms and produces a list with the particle selected by most of them.

Two new streaming protocols are under development and will join the described  pipeline in a near future. The first one will perform 2D classification and the second one will create a initial 3D map based on these classes. A first version of these protocols is available in the \scipion developers version.

As commented in Section \ref{overall}, to monitor, chart and create alerts  we have developed a set of metaprotocols. By default, \protocol{system}, \protocol{CTF} and \protocol{report monitors} are executed. \protocol{System monitor} reports on  CPU and GPU usage, memory consumption, and disk I/O. \protocol{CTF monitor} plots the CTF defocus and astigmatism  and it will raise an alarm if these parameters are not within a given range. Finally the \protocol{report} protocol pushes all the created plots and summaries to a web server so this information can be accessed by users who are not physically in the microscope room.

>>>>

In the following we describe the most important modifications made to \scipion to facilitate its deployment and execution in centralized facilities.

\subsection{Stream Processing}

Stream processing, i.e. computing on data directly as they are produced or received, is the main change introduced in \scipion. 
In this way, a new level of parallelization has been reached since the  data generated by the microscope continuously flows through a chain of protocols. For example, as movies are imported to the system they are aligned and their CTF is estimated. In \scipion version 1.2, users may find  the first steps in the image processing workflow adapted to streaming, including movie alignment,  CTF estimation and particle picking and extraction. In the developers version, several 2D classification algorithms are being adapted for this new way of processing.

%\scipion is a multilayered application, the first layer handles the interaction with the user (\emph{presentation layer}), the second saves and retrieves the data used by the application  (\emph{data layer}) and finally, the third layer (\emph{business layer}) process the data following the user instructions.  
\scipion stream implementation make extensive use of threads. %A thread is the smallest unit of processing that can be scheduled by an operating system. 
Using threads, a programmer can effectively create two or more tasks that run at the same time and share the protocol resources (e.g. memory). 
%is based on periodic updates of the protocol input and output data during the image processing. 
%Each protocol execution in \scipion is an independent process that can create processing threads. 
Each protocol that works in streaming mode has one of its threads monitoring input and updating output  data while other threads take care of the data processing. This clear separation between data access and data processing marks an important difference between running a script or using \scipion, since it facilitates a form of computing in which several jobs are executed  concurrently, instead of sequentially. Moreover, \scipion workflow engine allows users to modify the workflow on the fly without modifying a single line of code.
%In practice, the latter follows  a more general and extensible approach that allows users to modify the workflow on the fly without modifying a single code line. %Moreover, it also allows to quickly develop new workflows .

@@

The second set of metaprotocols are grouped under the name \emph{consensus}. For a given logical step (for example, particle picking) these protocols check 
the consistency of the output datasets obtained from the same input data using different algorithms. Continuing with the particle picking example, \protocol{consensus picking} will compare, at a given instant, the particles selected for each one of the executed particle-picking algorithms and produce as output a particle set containing those particles selected by most of the algorithms.

We would like to finish this section stressing that despite the modifications introduced to \scipion data and process model, the framework is backward compatible and keeps providing full data provenance. In other words, \scipion provides detailed information about the origin of the data  and the process to generate it.

@@

\scipion is a flexible framework that allows to create different workflows by choosing among many algorithms at each step. Although the best workflow for each case will depend on specific requirements of specimens, microscopes or facilities, we  described the pipeline offered by default at the \emph{National Center for Biotechnology} (CNB) cryoEM Facility as use case to clarify Scipion capabilities.

The workflow starts two independent protocols in parallel. The first protocol estimates the camera gain at each pixel for a few  movies \citep{sorzano2018}. % In the CNB setup the microscope camera is calibrated and internally performs the gain correction before writing the movies so the estimated gain image should be almost constant and equal to 1. 
The output of this protocol serves as verification of the validity of the experimental gain image for the whole data set. The second protocol performs direct detector movie alignment. Currently \scipion offers  five  methods for movie alignment: motioncorr \citep{Li2015}, motioncor2 \citep{Zheng2016:motioncor2}, correlation (an unpublished CPU version that implements in Xmipp a global alignment method and solves it similarly to motioncorr but using robust statistics), unblur \citep{Grant2015:unblur} and optical flow \citep{Abrishami2015:optical-flow}. Then the CTF of the resulting micrographs are calculated. Scipion provides three CTF estimation methods:
CTFFIND4 (Rohou and Grigorieff, 2015), gCTF (Zhang, 2016) and Xmipp CTF estimation (Sorzano et al., 2007; Vargas et al., 2013). At this point the user may compute the CTFs using several algorithms and compare them with the protocol \protocol{CTF consensus} that reports up to which frequency two estimations of the same micrograph are equivalent. Further automatic filtering based on CTF is available through the protocol \protocol{CTF filtering} that selects micrographs based on the astigmatism, resolution and defocus. %Another criteria for CTF selection is iciness, that is,  the ratio of the intensity in the resolution band between 3.5 and 3.9 \AA, and between 6 and 30 \AA, which gives a good estimate of the ice crystal content of the vitreous specimen.

Up to this point the image processing pipeline is quite solid and may be executed in streaming without user intervention. The next step is to select (pick) particles. We have recently adapted eight particle picking methods in \scipion  for streaming (see at \url{https://github.com/I2PC/scipion/wiki/Integrated-Protocols#particles} an exhaustive list). In this way,  particles may be selected as soon as any new micrograph is available. Some picking algorithms require a training step in which either user intervention or information from a previous selection is needed. The streaming functionality is separated from the picking logic, so if in the future a new algorithm is added, it will work in streaming without extra effort from the algorithm developer. For those users that execute several picking algorithms, the protocol \protocol{picking consensus} may be useful. \protocol{picking consensus}  calculates the agreement between different particle-picking algorithms and produces a list with the particles selected by most of them.

Two new streaming protocols are under development and will join the described  pipeline in a near future. The first one will perform 2D classification and the second one will create an initial 3D map based on these classes. A first version of these protocols is available in the \scipion developers version.

As commented in Section \ref{overall}, to monitor, chart and create alerts  we have developed a set of metaprotocols. By default, \protocol{system}, \protocol{CTF} and \protocol{report monitors} are executed. \protocol{System monitor} reports on  CPU and GPU usage, memory consumption, and disk I/O. \protocol{CTF monitor} plots the CTF defocus and astigmatism  and it will raise an alarm if these parameters are not within a given range. Finally, the \protocol{report} protocol pushes all the created plots and summaries to a web server. This information can be accessed by users who are not physically in the microscope room (a live example report is available at \url{http://nolan.cnb.csic.es/scipionbox/lastHTMLReport/}).

### 2018-04-23 3.workflow.tex
from home Marta (swedden) comments
I think this is done except for the cover letter

The data flow created by an electron microscope requires a careful design of the IT infrastructures.  Different facilities have adopted different solutions and therefore, how \scipion  access data and interchange information may require minor adjustments. In this section we discuss  the different solutions applied in the different facilities in which \scipion is running.

So far, \scipion is being used routinely in seven Cryo-EM facilities:
\begin{itemize}
 \itemsep0em

 %\item \emph{Ume\aa\ Core Facility for Electron Microscopy} (UCEM, \url{http://www.kbc.umu.se/english/ucem})[** Jose Miguel can you verify this?] 
 \item \emph{The Swedish National Cryo-EM Facility}. The Facility has two nodes: at \scilifelab in Stockholm and at Ume\aa\ University (\url{http://www.scilifelab.se}, \url{http://www.kbc.umu.se/english/ucem/cryo-em/})
 \item \emph{ESRF Cryo-Electron Microscope} (\url{http://www.esrf.eu/home/UsersAndScience/Experiments/MX/About_our_beamlines/CM01.html})
 \item \emph{eBIC at Diamond Light Source} ( \url{http://www.diamond.ac.uk/Science/Integrated-facilities/eBIC.html})
 \item \emph{CNB CryoEM Service} (\url{http://www.cnb.csic.es/index.php/en/research/core-facilities/microscopia-crioelectronica})
 \item \emph{Molecular Microscopy Consortium - NIH} (\url{https://www.niehs.nih.gov/research/atniehs/facilities/mmc/index.cfm})
 \item \emph{National Cancer Institute - NIH} (\url{https://www.cancer.gov/research/resources/cryoem})

@@

\scipion original design satisfied the requirements of the CNB, in which \scipion automatically fetches newly recorded movies from a network mounted disk. After this first installation, \scipion was deployed on SciLifeLab (a centralized facility located at Stockholm) where a rigorous booking system is followed. There, \scipion was adapted to interface with this booking platform in order to produce better reports. Lately,  \scipion has been installed in  large synchrotrons  such as ESRF and Diamond  where projects are handled by ISPyB (a customized laboratory information management system -LIMS- \citep{Delageniere2011:ispb}) and data are saved on a distributed file system. % that heavily penalizes access to lists of files. 
In this environment, \scipion needs to constantly interchange information with ISPyB and with other applications through a message queue system called \emph{ActiveQ}.% and it cannot longer check if there is a new file in a particular storage device but must wait to be informed by the system that a new file has been created.

>>>>

The data flow created by an electron microscope requires a careful design of the IT infrastructures.  Different facilities have adopted different solutions and therefore, how \scipion  access data and interchange information may require minor adjustments. In this section we discuss  the  solutions applied by the different facilities in which \scipion is running.

\scipion is so far being used routinely in seven Cryo-EM facilities:
\begin{itemize}
 \itemsep0em

 %\item \emph{Ume\aa\ Core Facility for Electron Microscopy} (UCEM, \url{http://www.kbc.umu.se/english/ucem})[** Jose Miguel can you verify this?] 
 \item \emph{The Swedish National Cryo-EM Facility}. The Facility has two nodes, at \scilifelab in Stockholm and at Ume\aa\ University (\url{http://www.scilifelab.se}, \url{http://www.kbc.umu.se/english/ucem/cryo-em/})
 \item \emph{ESRF Cryo-Electron Microscope} (\url{http://www.esrf.eu/home/UsersAndScience/Experiments/MX/About_our_beamlines/CM01.html})
 \item \emph{eBIC at Diamond Light Source} ( \url{http://www.diamond.ac.uk/Science/Integrated-facilities/eBIC.html})
 \item \emph{CNB CryoEM Service} (\url{http://www.cnb.csic.es/index.php/en/research/core-facilities/microscopia-crioelectronica})
 \item \emph{Molecular Microscopy Consortium - NIH} (\url{https://www.niehs.nih.gov/research/atniehs/facilities/mmc/index.cfm})
 \item \emph{National Cancer Institute - NIH} (\url{https://www.cancer.gov/research/resources/cryoem})

@@

\scipion original design satisfied CNB requirements, in which \scipion automatically fetches newly recorded movies from a network mounted disk. After this first installation, \scipion was deployed on SciLifeLab (a centralized facility located at Stockholm), where a rigorous booking system is followed. There, \scipion was adapted to interface with this booking platform to produce better reports. Lately,  \scipion has been installed in  large synchrotrons  such as ESRF and Diamond,  where projects are handled by ISPyB (a customized laboratory information management system -LIMS- \citep{Delageniere2011:ispb}) and data are saved on a distributed file system. % that heavily penalizes access to lists of files. 
In this environment, \scipion needs to constantly interchange information with ISPyB and with other applications through a message queue system called \emph{ActiveQ}.% and it cannot longer check if there is a new file in a particular storage device but must wait to be informed by the system that a new file has been created.

### 2018-04-23 3.workflow_cnb.tex
I think this is done except for the cover letter

At the beginning CNB networking setup was a quite straightforward one, movies where stored in the  same machine that ran \scipion and processed data were saved to external USB hard disks by this same machine. The situation changed when the new Falcon-III detector was installed. After that, data were produced at sustained speeds as high as 90 MB/sec (when acquiring four movies by hole in lineal mode) and the main problem became to move smoothly the data through the entire pipeline from the microscope to the final user laboratory. In the following we describe such a pipeline.

@@

The data flow is a follows: (a) the microscope system stores movies in the microscope-NAS, (b) when executing alignment-movie protocols \scipionbox will temporary read the movies from 
the microscope-NAS but will not store them locally, (c) each hour, output-NAS will connect to \scipionbox and copy -or update- the last \scipion project, (d) at the same time output-NAS may be either executing a script to incrementally backup \scipion project and the movies to a USB disk or serve this information through the Internet and, (e) in parallel, \scipionbox transfers to  output-NAS different HTML reports that may be checked by users or staff with a HTML browser (see \url{http://nolan.cnb.csic.es/scipionbox}).

Although CNB staff try to discourage the use of external USB hard disks versus network as way of retrieving the raw and processed data, this is the preferred option for most users.
USB 3.0 drives can theoretically handle data flows of 300 MB/s, but CNB experience is that, in this busy environment, many of them  have trouble exceeding 50 MB/s. In most cases, 50 MB/s is enough to transfer the data before the following microscope shift starts. Nevertheless, real-world is tough and it happens that two, or even three,  users try to download their data simultaneously. Fortunately, output-NAS works as front-end and isolates the data acquiring and processing infrastructure from the user downloading. Network users access to output-NAS using a chrooted common account. This account only allows rsync connections and make impossible to retrieve data if the name of the project to be downloaded is unknown. In order to speed up transfer, weak ciphers (as \emph{arcfour}) has been activated in output-NAS.

@@

\emadmin was born as a script that created a normalized tree of directories  
where movies acquired by the microscope could be stored, helped users to choose between a few predetermined image processing workflows and finally launched \scipion. At present it has grown in a client-server application that in addition to the old script capacities has incorporated the following functions:

\begin{enumerate}
 \item Transparent addition of new workflows. \scipion is able to export any executed workflow as a json file. \emadmin can import this files and use them to create new predetermined workflows.
 \item Automatic creation of pdf user's report containing: microscope acquisition parameters and histograms summarizing data resolution and  defocus. 
 \item The above mentioned information is stored in a database for further analysis. By default the system plots the  average resolution and astigmatism of the different acquisitions versus time.
 \item Remote management. \emadmin is a client server application, the client maybe executed in a machine different from the one that executes \scipion.
 \item Automatic backup of the \scipion project.
 \item \scipion is able to create live HTML reports on the image acquisition process. \emadmin keeps track of all of them and facilitates the access to this information.
\end{enumerate}

\emadmin is free software available at github repository (\url{https://github.com/rmarabini/webservices/tree/master/EMadmin}). You are welcomed to try it but be aware that \emadmin is designed to be used at CNB and therefore, no support is provided for it.

>>>>

At the beginning CNB networking setup was a quite straightforward one, movies where stored in the  same machine that ran \scipion and processed data were saved to external USB hard disks by this same machine. The situation changed when the new Falcon-III detector was installed. After that, data were produced at sustained speeds as high as 90 MB/sec (when acquiring four movies by hole in linear mode) and the main problem became to move smoothly the data through the entire pipeline from the microscope to the final user laboratory. In the following we describe such a pipeline.

@@

The data flow is a follows: (a) the microscope system stores movies in the microscope-NAS, (b) when executing alignment-movie protocols \scipionbox reads the movies from the microscope-NAS but does not store them locally, (c) each hour, output-NAS connects to \scipionbox and copy -or update- the last \scipion project, (d) at the same time output-NAS may be either executing a script to incrementally backup \scipion project and the movies to a USB disk or serve this information through the Internet and, (e) in parallel, \scipionbox transfers to  output-NAS different HTML reports that may be checked by users or staff with a HTML browser (see \url{http://nolan.cnb.csic.es/scipionbox/lastHTMLReport/}).

Although CNB staff try to discourage the use of external USB hard disks versus network as way of retrieving the raw and processed data, this is the preferred option for most users.
USB 3.0 drives can theoretically handle data flows of 300 MB/s, but CNB experience is that, in this busy environment, many of them  have trouble exceeding 50 MB/s. In most cases, 50 MB/s is enough to transfer the data before the following microscope  turn-shift starts. When two, or even three, users try to download their
data simultaneously, output-NAS works as front-end and isolates the data
acquiring and processing infrastructure from the user’s downloading activities.
Network users access to output-NAS using a hardened common account. This account only allows rsync connections and make impossible to retrieve data if the name of the project to be downloaded is unknown. Weak ciphers (as arcfour) has been activated in outputNAS to speed up transfer.

@@

\emadmin was born as a script that created a normalized tree of directories  
where movies acquired by the microscope could be stored, helped users to choose between a few predetermined image processing workflows and finally launched \scipion. At present it has grown in a client-server application that, in addition to the old script capabilities, has incorporated the following functions:

\begin{enumerate}
 \item Transparent addition of new workflows. \scipion is able to export any executed workflow as a json file. \emadmin can import this files and use them to create new predetermined workflows.
 \item  Automatic creation of pdf user’s report that contains microscope acquisition parameters and histograms summarizing data resolution and defocus. 
 \item The above mentioned information is stored in a database for further analysis. By default, the system plots the  average resolution and astigmatism of the different acquisitions versus time.
 \item Remote management. \emadmin is a client server application, the client maybe executed in a machine different from the one that executes \scipion.
 \item Automatic backup of the \scipion project.
 \item \scipion is able to create live HTML reports on the image acquisition process. \emadmin keeps track of all of them and facilitates the access to this information.
\end{enumerate}

\emadmin is free software available at github repository (\url{https://github.com/rmarabini/webservices/tree/master/EMadmin}). You are welcomed to download and customize it to meet your organization specific requirements.

### 2018-04-23 3.workflow_diamond.tex
I think this is done except for the cover letter

Diamond has thousands of users every year, both academic and commercial, and it is vital that their data is kept secure and confidential. A user management system has been developed which allocates each user with a unique federal identity (IDs), and associates those user IDs with the experiments in which they partake in. Visits are structured such that all raw and processed data collected during an experiment are kept in one directory, and only the associated visitors have read and write permissions in that directory. Users may access their data through ISPyB \citep{Delageniere2011:ispb},  a Laboratory Information Management System (LIMS) combining sample tracking and experiment reporting. %The link between the user and their visits enables data management such as archiving data to a long-term tape storage system, or the Laboratory Information Management System ISPyB (REF. Delageniere et al Bioinformatics 2011). In contrast to the CNB setup, Diamond has integrated the microscopes in much the same fashion to that of the beamlines at the facility, as is shown in figure X

@@

Diamond IT infrastructure is complex and requires to integrate a large collection of heterogeneous systems. In this environment a major problem is to achieve interaction and data exchange between diverse applications. One of the solutions to this problem has been to implement \emph{indirect communication} through a message queuing system called \emph{ActiveQ}. A message queue is a mechanism
that allows a sender process and a receiver process to exchange information; instead of connecting directly, the sender posts messages in a queue and the receiver, when ready, takes these messages from the queue and process them appropriately.

@@

\subsection{Additional Software Developments: ISyB monitor, Scipion Headless}

From the image processing point of view, in Diamond, a typical cryoEM session starts by launching a custom made script that  allows users to specify values pertinent to their experiment, namely the session ID (or visit number), which microscope they are using, and several other key data collection parameters. Once set, a file describing a \scipion workflow is created and then saved to disk.
A daemon that is running on the microscope control server notices the file creation and send a ``file creation'' message to \emph{ActiveMQ}.

Another process listening to \emph{ActiveMQ} then launches \scipion from this workflow and creates a running ``headless'' project. \scipion headless mode has been developed specifically for eBIC and allows \scipion to be executed without user interface in large clusters with no graphical board.

@@

To monitor the progress of the automatic image processing, CNB and \scilifelab cryo-EM services make use of \scipion default monitor system. However, in Diamond, the electronic notebook ISPyB is the standard tool to record and show metadata about the different experiments. In this way, a new monitor has been developed which, through a ISPyB python API, allows \scipion to directly interface with ISPyB.  This setup provides the users with a web interface showing general metadata about their experiment as well as  real-time updates on steps of the process and relevant output such as motion corrected images, drift values, CTF images, etc.

>>>>

Diamond has thousands of users every year, both academic and commercial, and it is vital that their data is kept secure and confidential. A user management system
has been developed to allocate each user with a unique federal identity (ID),
and to associate this ID with the experiments in which the user partake in.
 Visits are structured such that all raw and processed data collected during an experiment are kept in one directory, and only the associated visitors have read and write permissions in that directory. Users may access their data through ISPyB \citep{Delageniere2011:ispb},  a Laboratory Information Management System (LIMS) combining sample tracking and experiment reporting. %The link between the user and their visits enables data management such as archiving data to a long-term tape storage system, or the Laboratory Information Management System ISPyB (REF. Delageniere et al Bioinformatics 2011). In contrast to the CNB setup, Diamond has integrated the microscopes in much the same fashion to that of the beamlines at the facility, as is shown in figure X

@@

 The complexity of Diamond IT infrastructure requires to integrate many heterogeneous systems. In this environment a major problem is to achieve interaction and data exchange between diverse applications. One of the solutions to this problem has been to implement \emph{indirect communication} through a message queuing system called \emph{ActiveQ}. A message queue is a mechanism
that allows a sender process and a receiver process to exchange information; instead of connecting directly, the sender posts messages in a queue and the receiver, when ready, takes these messages from the queue and process them appropriately.

@@

\subsection{Additional Software Developments: ISPyB monitor, Scipion Headless}

From the image processing point of view, in Diamond, a typical cryoEM session starts by launching a custom made script that  allows users to specify values pertinent to their experiment, namely the session ID (or visit number), which microscope they are using, and several other key data collection parameters. Once set, a file describing a \scipion workflow is created and then saved to disk.
A daemon that is running on the microscope control server notices the file creation and sends a ``file creation'' message to \emph{ActiveMQ}.

Another process listening to \emph{ActiveMQ} then launches \scipion from this workflow and creates a running ``headless'' project. \scipion headless mode has been developed specifically for eBIC and allows \scipion to be executed without graphical user interface in large clusters with no graphical board.

@@

Unlike CNB and SciLifeLab cryo-EM services, where the
Scipion default monitor system displays the progress of the automatic image
processing, in Diamond, the electronic notebook ISPyB is the natural framework
to record and show metadata about the different experiments. A new monitor has thus been developed to allow Scipion to directly interface with ISPyB using the ISPyB python API.
%To monitor the progress of the automatic image processing, CNB and \scilifelab cryo-EM services make use of \scipion default monitor system. However, in Diamond, the electronic notebook ISPyB is the standard tool to record and show metadata about the different experiments. 
%In this way, a new monitor has been developed which, through a ISPyB python API, allows \scipion to directly interface with ISPyB.  
This setup provides the users with a web interface showing general metadata about their experiment, as well as  real-time updates on steps of the process and relevant output, such as motion corrected images, drift values, CTF images, etc.
